Stage-structured evolutionary demography for simultaneous hermaphrodites with partial selfing

### 2020-07-10 notes/notes-SA-partSelf-wDemography.tex
Update notes-SA-partSelf-wDemography.tex

{
 \begin{align*} \label{eq:M22}
	\mbf{M}_{22} = 
		\frac{1}{\lambda_{AA}}\left(\begin{array}{cc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime
			\end{array} \right), \numberthis
\end{align*}
}
where 
\begin{equation}
  \mbox{p}_{n}=\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \left( \hat{\mathbf{p}}^S_{AA}+\hat{\mathbf{p}}^X_{AA} \right)	
\end{equation}

@@

{
\begin{align*} \label{eq:eigAA}
	\tilde{\zeta}_{AA} = 
		\frac{1}{\lambda_{AA}}\rho\left(\begin{array}{cc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime
			\end{array} \right). \numberthis
\end{align*}
}

@@

\begin{equation} \label{eq:coexist_AA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime
			\end{array} \right)., \\ 
\end{equation}

\begin{equation} \label{eq:coexist_aa}
	\lambda_{aa} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2\mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2\mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime
			\end{array} \right).\\ 
\end{equation}

@@

And the coexistence conditions become:
\begin{equation} \label{eq:coexist_AA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{c}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{\mbf{F}_{AA}\hat{\mbf{p}}_{AA}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \hat{\mathbf{p}}_{AA}	}
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_AA}
	\lambda_{aa} < 
			\rho\left(\begin{array}{c}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2 } (1 - C_{aa})\frac{\mbf{F}_{aa}\hat{\mbf{p}}_{aa}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{aa}^\prime \hat{\mathbf{p}}_{aa}	}
			\end{array} \right). \\ 
\end{equation} 
\end{landscape}

@@

And the coexistence conditions become:
\begin{eqnarray} \label{eq:coexist_AA}
\lambda_{AA}> 
			\rho\left(\left(
					\begin{array}{cc}
						\sigma_{Aa}(1 - \gamma_{Aa}) & 0 \\
						\sigma_{Aa} \gamma_{Aa}     & s_{Aa}
					\end{array}
				\right)   + \frac{1}{2} (1 - C_{Aa}) \left(
					\begin{array}{cc}
						0 &  f_{Aa} \\
						0 & 0
					\end{array}
				\right) +\frac{1}{2} (1 - C_{AA})\frac{f^\prime_{Aa}}{f^\prime_{AA}}\left(
					\begin{array}{cc}
						0 &  f_{AA} \\
						0 & 0
					\end{array}
				\right)\right). 
\end{eqnarray}

>>>>

{
\footnotesize
 \begin{align*} \label{eq:M22}
	\mbf{M}_{22} = 
		\frac{1}{\lambda_{AA}}\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \numberthis
\end{align*}
}
where 
\begin{equation}
  \mbox{p}_{n}=\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \left( \hat{\mathbf{p}}^S_{AA}+\hat{\mathbf{p}}^X_{AA} \right)	
\end{equation}

@@

{
\footnotesize
\begin{align*} \label{eq:eigAA}
	\tilde{\zeta}_{AA} = 
		\frac{1}{\lambda_{AA}}\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right). \numberthis
\end{align*}
}

@@

{\footnotesize
\begin{equation} \label{eq:coexist_AA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{AA})\mbf{F}_{AA} \big(\hat{\mbf{p}}_{X,AA}+ \hat{\mbf{p}}_{S,AA}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{aa})\mbf{F}_{aa}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_AA}
	\lambda_{aa} < 
			\rho\left(\begin{array}{ccc}
\mathbf{U}^S_{Aa} +\frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & 0 \\
 \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa}+\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime &\mathbf{U}^X_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2  \mbox{p}_{n}} (1 - C_{aa})\mbf{F}_{aa} \big(\hat{\mbf{p}}_{X,aa}+ \hat{\mbf{p}}_{S,aa}  \big) \otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime & (1-C_{AA})\mbf{F}_{AA}\\
  \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{AA} +C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation} 
}

@@

\hl{This is a guess, I have not worked through the actual algebra yet} And the coexistence conditions become:
\begin{equation} \label{eq:coexist_bigAA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{\mbf{F}_{AA}\hat{\mbf{p}}_{AA}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \hat{\mathbf{p}}_{AA}	} & (1-C_{aa}) \mbf{F}_{aa} \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_baa}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{aa})\frac{\mbf{F}_{aa}\hat{\mbf{p}}_{aa}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{aa}^\prime \hat{\mathbf{p}}_{aa}	} & (1-C_{AA}) \mbf{F}_{AA} \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}^S_{AA} +C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation} 
\end{landscape}

@@

And the invasion condition becomes (\hl{based on my earlier guess, so still an (educated?) guess}):

\begin{eqnarray} \label{eq:coexist_AA}
\lambda_{AA}> 
			\rho\left(
					\begin{array}{cc|cc}
						\sigma_{Aa}(1 - \gamma_{Aa}) &  \frac{1}{2} (1 - C_{Aa}) f_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{f^\prime_{Aa}f_{AA}}{f^\prime_{AA}} &0 & (1-C_{aa})f_{aa}\\
						\sigma_{Aa} \gamma_{Aa}     & s_{Aa}& 0 & 0\\ \hline
							0 & \frac{1}{4}C_{Aa}(1-\delta)f_{Aa} &\sigma_{aa}(1 - \gamma_{aa})  & C_{aa}(1-\delta)f_{aa}\\
								0 & 0 & \sigma_{aa} \gamma_{aa}     & s_{aa}
					\end{array}
				\right). 
\end{eqnarray}
